\vspace{-0.75in} Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-06-08 main.tex
Explained crossover point.  Giving up on re-runing experiments.
Added authors for submission as tech report.

% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

%\title{Accelerating $\ell_1$-Minimization Using Many-Core CPUs/GPUs \\ and Application to Face Recognition
%\title{Efficient Parallelization of Sparse Representation for Face Recognition}
%\thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}}
%\title{Many-Core Parallelization of $\ell_1$-Minimization for Face Recognition
\title{\vspace{-0.2in} Parallelization of Fast $\ell_1$-Minimization for Face Recognition}
%\title{Parallelization of Fast $\ell_1$-Minimization Towards Real-Time Face Recognition}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\small\url{http://www.author.org/~second}}
}

@@

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The $x$-axis represents the size of the $A$ matrix and the $y$-axis represents the
average amount of time to complete a single problem instance.  The GPU
implementation tends to be faster than the CPU implementation at solving a
single large problem, whereas the CPU implementation is faster at solving a
single small problem.  The transition between the two regimes occurs (at 2000) where
the problem size begins to exceed the size of the CPU L3 cache. 
\begin{figure}
\begin{center}
\includegraphics[width=2.5in]{figures/time_vs_matrix_size_constant_tol}
\end{center} \vspace{-0.1in}
\caption{\small Comparison of $\ell_1$-min runtime vs. dimensions of $A$ on random data.} \vspace{-0.1in}
\label{fig:random_data}
\end{figure}

>>>>

\cvprfinalcopy % *** Uncomment this line for the final submission

@@

\title{\vspace{-0.75in} Parallelization of Fast $\ell_1$-Minimization for Face Recognition}

% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both

\author{Andrew Wagner\\
University of Illinois at Urbana-Champaign\\
{\small awagner@illinois.edu}
\and
Victor Shia\\
University of California Berkeley\\
{\small vshia@eecs.berkeley.edu}
\and
Allen Yang\\
{\small yang@eecs.berkeley.edu}
\and
Mark Murphy\\
{\small mjmurphy@eecs.berkeley.edu}
\and
Yi Ma\\
University of Illinois at Urbana-Champaign\\
{\small yima@illinois.edu}
}

@@

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The $x$-axis represents the size of the $A$ matrix and the $y$-axis represents the
average amount of time to complete a single problem instance.  The GPU
implementation tends to be faster than the CPU implementation at solving a
single large problem, whereas the CPU implementation is faster at solving a
single small problem.  The transition between the two regimes occurs where the size of
$A$ reaches $2000 \times \1000 \times 4 = 8$ MB, i.e. the size of the CPU L3 cache. 
\begin{figure}
\begin{center}
\includegraphics[width=2.5in]{figures/time_vs_matrix_size_constant_tol}
\end{center} \vspace{-0.1in}
\caption{\small Comparison of $\ell_1$-min runtime vs. dimensions of $A$ on random data.} \vspace{-0.1in}
\label{fig:random_data}
\end{figure}
